Comb associative operads

### 2018-08-27 CAs_operads.tex
Maj Intro et bib

In order to show that the $\left(\CAsAll, \OrdCAs\right)$ extends into a
lattice, we relate $\left(\CAsAll, \OrdCAs\right)$ with the lattice of
integers $\left(\N,\mid, \gcd, \lcm\right)$, where $\mid$ denotes the
division relation, $\gcd$ denotes the greatest common divisor, and
$\lcm$ the least common multiple operators, respectively.

>>>>

In order to show that $\left(\CAsAll, \OrdCAs\right)$ extends into a
lattice, we relate $\left(\CAsAll, \OrdCAs\right)$ with the lattice of
integers $\left(\N,\mid, \gcd, \lcm\right)$, where $\mid$ denotes the
division relation, $\gcd$ denotes the greatest common divisor, and
$\lcm$ the least common multiple operators, respectively.

### 2018-08-27 Introduction.tex
Maj Intro et bib

A first connection between the associative operad and the Tamari order
is based upon the fact that the orientation of~\eqref{equ:congruence_as}
from left to right provides a convergent orientation (a terminating and
confluent rewrite relation) of the congruence $\Congr$. The normal
forms of the rewrite relation induced by the rewrite rule obtained by
orienting~\eqref{equ:congruence_as} from left to right are right comb
binary trees and are hence in one-to-one correspondence with the
elements of~$\As$.
\medbreak

>>>>

A first connection between the associative operad and the Tamari order
is based upon the fact that the orientation of~\eqref{equ:congruence_as}
from left to right provides a convergent orientation (a terminating and
confluent rewrite relation) of the congruence $\Congr$. The normal
forms of the rewrite relation induced by the rewrite rule obtained by
orienting~\eqref{equ:congruence_as} from left to right are right comb
binary trees and are hence in one-to-one correspondence with the
elements of~$\As$. Following the ideas developed by Anick for
associative algebras~\cite{Ani86}, the description of an operad by mean
of normal forms provides homological information for this operad. One of
the fundamental homological properties for operads is
Koszulity~\cite{GK94}, generalizing Koszul associative
algebras~\cite{Pri70}: the convergent orientation of $\As$ proves that
it is a Koszul operad~\cite{LV12}.
\medbreak
